Parametricity for Primitive Nested Types and GADTs

### 2020-12-26 free-theorems-nesteds/20-mscs.tex
finished Sec 8

To prove Equation~\ref{eq:part-one} we first observe that

@@

gives that, for all $\ol{R : \rel_0}$ and $\ol{m : \relsem{\Gamma;
    \ol\alpha \vdash K}\rho[\ol{\alpha := R}] \to \relsem{\Gamma; \Phi
    \vdash A}\rho'}$,

@@

Equation~\ref{eq:cocone-proj} {\color{red} and its analogue for
  $\iota'$ and $j'$ then give --- HOW?????}

@@

    \vdash A}\rho'} \Big) \,\circ\, {\color{red} j?}f_{\ol{\pi_i R},

@@

@@

@@

{\color{red} Equation~\ref{eq:cocone-proj} and its analogue for
  $\iota'$ and $j'$ then give}

>>>>

To prove Equation~\ref{eq:part-one} we first observe that the
morphisms $\iota'_{\ol{R}, \ol{m}} \,\circ\, \relsem{\Gamma; \Phi,
  \ol\alpha \vdash F}f[\ol{\alpha := \id_R}]$ form a cocone for
with vertex 
The universal property (Equation~\ref{eq:cocone-def}) of

@@

therefore gives that, for all $\ol{R : \rel_0}$ and $\ol{m :
  \relsem{\Gamma; \ol\alpha \vdash K}\rho[\ol{\alpha := R}] \to
  \relsem{\Gamma; \Phi \vdash A}\rho'}$,

@@

Equation~\ref{eq:cocone-proj} and its analogue for
  $\iota'$ and $j'$ then give 

@@

    \vdash A}\rho'} \Big) \,\circ \, k \,\circ\, j_{\ol{\pi_i R},

@@

&  = & \pi_i \Big( \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma;
\,\circ\, k \,\circ\, h \,\circ \,\pi_i \iota_{\ol{R}, \ol{m}} \\[2ex]
& = & \pi_i \Big( \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma;
f)[\ol{\alpha := \id_{\pi_i R}}]\\[2ex]
& = & k' \, \circ \, h'\,\circ\,\pi_i \iota'_{\ol{R},
f)[\ol{\alpha := \id_{\pi_i R}}]\\[2ex]
& = & k' \,\circ \, j'_{\ol{\pi_i R}, \ol{\pi_i m}} \,\circ\, \setsem{\Gamma; \Phi,

@@

Since both $k$ and $k'$ are isomorphisms, we have that, up to
isomorphism, 
    \vdash A}\rho'} \Big) \circ\, j_{\ol{\pi_i R},

@@

Equation~\ref{eq:cocone-proj} and its analogue for
  $\iota'$ and $j'$ then give that, up to isomorphism,
